Visualizations for the manuscript

### 2022-04-05 metanalysis_visualization/manuscript_Figures.Rmd
Subcases count fix

perc_disorder_group_total_fix <- perc_disorder_group_complete %>%
  group_by( time_p, disorder_group ) %>%
  summarise( total_diagnoses = sum(count_icd, na.rm = TRUE),
             sum_dg_psy = sum(count_dg),
             percentage = (sum_dg_psy / total_diagnoses) * 100, 
             country = "ALL")

@@

### Disorder group 
```{r}
perc_disorder_group_total_first <- perc_disorder_group_all %>%
  select( - percentage_dg ) %>%
  group_by( time_p, disorder_group ) %>%
  mutate( total_cases = sum( count_icd, na.rm = TRUE ), 
          dg_cases = sum( count_dg ), 
          percentage = 100* dg_cases / total_cases, 
          country = "ALL")

perc_disorder_group_total_first %>%
  ggplot( aes( x= as.Date( time_p ), y = percentage, group = disorder_group )) +
  facet_wrap( ~ disorder_group, scales = "free" ) +
  geom_line( aes(color = disorder_group )) +
  geom_point( aes( color = disorder_group )) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed")+
  labs(x ="", y = "percentage of patients (%)")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA))

percentages_htm <- perc_disorder_group_total_first %>%
  select( time_p, disorder_group, percentage ) %>%
  unique() %>%
  pivot_wider( names_from =  disorder_group, 
               values_from = percentage )

@@

counts_htm <- perc_disorder_group_total_first %>%
  select( time_p, disorder_group, dg_cases ) %>%
  unique() %>%
  pivot_wider( names_from =  disorder_group, 
               values_from = dg_cases )
counts_htm <- counts_htm[  , -1]

tempVariabilityInput <- new('DataTemporalMap', probabilityMap = as.matrix(percentages_htm), 
         countsMap = as.matrix(counts_htm), dates = dates, support = as.data.frame(names(percentages_htm)), 
         variableName = "example", variableType = "character", period = "month")

@@

#### facet wrap in 3 groups based on %
### most prevalent
perc_disorder_group_total_first %>%
  filter(disorder_group %in% c("Anxiety Disorders", "Depressive Disorders", "Suicide or Self-Injury" ))  %>%
  ggplot( aes( x= as.Date( time_p ), y = percentage, group = country )) +
  facet_wrap( ~ disorder_group ) +
  geom_line( aes(color = country )) +
  geom_point( aes( color = country )) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed")+
  labs(x ="", y = "percentage of patients (%)")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA)) +
  scale_color_manual( values = cbPalette )

#medium prevalent
perc_disorder_group_total_first %>%
  filter(disorder_group %in% c("Trauma and Stressor-Related Disorders", "Mental Health Symptom", "Disruptive, Impulse Control and Conduct Disorders", 
                               "Feeding and Eating Disorders"))  %>%
  ggplot( aes( x= as.Date( time_p ), y = percentage, group = country )) +
  facet_wrap( ~ disorder_group ) +
  geom_line( aes(color = country )) +
  geom_point( aes( color = country )) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed")+
  labs(x ="", y = "percentage of patients (%)")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA)) +
  scale_color_manual( values = cbPalette )

#low prevalent
perc_disorder_group_total_first %>%
  filter(disorder_group %in% c("Miscellaneous", "Substance-Related and Addictive Disorders", 
                               "Personality Disorders", "Bipolar and Related Disorders", "Sleep-Wake Disorders", 
                               "Schizophrenia Spectrum and Other Psychotic Disorders", "Somatic Symptom and Related Disorders", 
                               "Obsessive-Compulsive and Related Disorders", "Dissociative Disorders" ))  %>%
  ggplot( aes( x= as.Date( time_p ), y = percentage, group = country )) +
  facet_wrap( ~ disorder_group ) +
  geom_line( aes(color = country )) +
  geom_point( aes( color = country )) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed")+
  labs(x ="", y = "percentage of patients (%)")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA)) +
  scale_color_manual( values = cbPalette )

perc_disorder_group_total_first %>%
  filter(disorder_group %in% c("Anxiety Disorders", "Depressive Disorders", "Suicide or Self-Injury" ))  %>%
  ggplot( aes( x= as.Date( time_p ), y = percentage, group = country )) +
  facet_wrap( ~ disorder_group ) +
  geom_line( aes(color = country )) +
  geom_point( aes( color = country )) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed") +
  labs(x ="", y = "percentage of patients (%)")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0)) +
  scale_color_manual( values = cbPalette ) + 
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6), 
        strip.text = element_text(size = 10, face = "bold"),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), strip.background = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA), 
        legend.position="bottom")

perc_disorder_group_total_first %>%
  filter( disorder_group %in% c("Anxiety Disorders", "Depressive Disorders", "Suicide or Self-Injury", 
  "Mental Health Symptoms", "Feeding and Eating Disorders" )) %>%
  ggplot( aes( x= as.Date( time_p ), y = percentage, group = country )) +
  geom_line( aes(linetype = country, color = country )) +
  geom_point( aes( shape= country, color = country )) +
  #scale_y_continuous(breaks = seq(0, 30, by = 5)) +
  facet_wrap2("disorder_group", axes = "all", scales ="free") + 
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed") +
  labs(x ="", y = "percentage of patients (%)")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0)) +
  scale_color_manual( values = cbPalette ) + 
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6), 
        strip.text = element_text(size = 10, face = "bold"),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), strip.background = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA), 
        legend.position="bottom")

@@

### Estimate number of ICD codes per site and disorder group
Represent this in 16 pannels, if we put all together, due to the different scales we will not be able to really see the differences between results. 
```{r}
mental_codes_qc_output_all <- mental_codes_qc_output_all %>%
    mutate( concept_code = gsub("[.]", "", concept_code ) ) %>%
  unique()

>>>>

perc_disorder_group_total <- perc_disorder_group_complete %>%
  group_by( time_p, disorder_group ) %>%
  summarise( total_diagnoses = sum(count_icd, na.rm = TRUE),
             dg_cases = sum(count_dg),
             percentage = (dg_cases / total_diagnoses) * 100, 
             country = "ALL")

@@

### Disorder group 
```{r}
perc_disorder_group_total %>%
  ggplot( aes( x= as.Date( time_p ), y = percentage, group = disorder_group )) +
  facet_wrap( ~ disorder_group, scales = "free" ) +
  geom_line( aes(color = disorder_group )) +
  geom_point( aes( color = disorder_group )) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed")+
  labs(x ="", y = "percentage of patients (%)")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA))

percentages_htm <- perc_disorder_group_total %>%
  select( time_p, disorder_group, percentage ) %>%
  unique() %>%
  pivot_wider( names_from =  disorder_group, 
               values_from = percentage )

@@

counts_htm <- perc_disorder_group_total %>%
  select( time_p, disorder_group, dg_cases ) %>%
  unique() %>%
  pivot_wider( names_from =  disorder_group, 
               values_from = dg_cases )
counts_htm <- counts_htm[  , -1]
tempVariabilityInput <- new('DataTemporalMap', probabilityMap = as.matrix(percentages_htm), 
         countsMap = as.matrix(counts_htm), dates = dates, support = as.data.frame(names(percentages_htm)), 
         variableName = "example", variableType = "character", period = "month")

@@

#### facet wrap in 3 groups based on %
### most prevalent
perc_disorder_group_total %>%
  filter(disorder_group %in% c("Anxiety Disorders", "Depressive Disorders", "Suicide or Self-Injury" ))  %>%
  ggplot( aes( x= as.Date( time_p ), y = percentage, group = country )) +
  facet_wrap( ~ disorder_group ) +
  geom_line( aes(color = country )) +
  geom_point( aes( color = country )) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed")+
  labs(x ="", y = "percentage of patients (%)")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA)) +
  scale_color_manual( values = cbPalette )

#medium prevalent
perc_disorder_group_total %>%
  filter(disorder_group %in% c("Trauma and Stressor-Related Disorders", "Mental Health Symptom", "Disruptive, Impulse Control and Conduct Disorders", 
                               "Feeding and Eating Disorders"))  %>%
  ggplot( aes( x= as.Date( time_p ), y = percentage, group = country )) +
  facet_wrap( ~ disorder_group ) +
  geom_line( aes(color = country )) +
  geom_point( aes( color = country )) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed")+
  labs(x ="", y = "percentage of patients (%)")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA)) +
  scale_color_manual( values = cbPalette )

#low prevalent
perc_disorder_group_total %>%
  filter(disorder_group %in% c("Miscellaneous", "Substance-Related and Addictive Disorders", 
                               "Personality Disorders", "Bipolar and Related Disorders", "Sleep-Wake Disorders", 
                               "Schizophrenia Spectrum and Other Psychotic Disorders", "Somatic Symptom and Related Disorders", 
                               "Obsessive-Compulsive and Related Disorders", "Dissociative Disorders" ))  %>%
  ggplot( aes( x= as.Date( time_p ), y = percentage, group = country )) +
  facet_wrap( ~ disorder_group ) +
  geom_line( aes(color = country )) +
  geom_point( aes( color = country )) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed")+
  labs(x ="", y = "percentage of patients (%)")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA)) +
  scale_color_manual( values = cbPalette )

perc_disorder_group_total %>%
  filter(disorder_group %in% c("Anxiety Disorders", "Depressive Disorders", "Suicide or Self-Injury" ))  %>%
  ggplot( aes( x= as.Date( time_p ), y = percentage, group = country )) +
  facet_wrap( ~ disorder_group ) +
  geom_line( aes(color = country )) +
  geom_point( aes( color = country )) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed") +
  labs(x ="", y = "percentage of patients (%)")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0)) +
  scale_color_manual( values = cbPalette ) + 
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6), 
        strip.text = element_text(size = 10, face = "bold"),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), strip.background = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA), 
        legend.position="bottom")

perc_disorder_group_total %>%
  filter( disorder_group %in% c("Anxiety Disorders", "Depressive Disorders", "Suicide or Self-Injury", 
  "Mental Health Symptoms", "Feeding and Eating Disorders" )) %>%
  ggplot( aes( x= as.Date( time_p ), y = percentage, group = country )) +
  geom_line( aes(linetype = country, color = country )) +
  geom_point( aes( shape= country, color = country )) +
  #scale_y_continuous(breaks = seq(0, 30, by = 5)) +
  facet_wrap2("disorder_group", axes = "all", scales ="free") + 
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed") +
  labs(x ="", y = "percentage of patients (%)")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0)) +
  scale_color_manual( values = cbPalette ) + 
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6), 
        strip.text = element_text(size = 10, face = "bold"),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), strip.background = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA), 
        legend.position="bottom")

@@

### Estimate number of ICD codes per site and disorder group
Represent this in 16 pannels, if we put all together, due to the different scales we will not be able to really see the differences between results.

```{r}
mental_codes_qc_output_all <- mental_codes_qc_output_all %>%
    mutate( concept_code = gsub("[.]", "", concept_code ) ) %>%
  unique()
